---
title: "Module 1"
author: "Erik Rehnberg Steeb"
date: "9/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Module 1 Instructions

This module is fairly straightforward and involves obtaining/downloading the dataset and writing functions to clean up some of the variables. The dataset is in tab-delimited format and can be read in using the read_delim() function in the readr package.

After downloading and reading in the dataset, the overall task for this module is to write a function named eq_clean_data()that takes raw NOAA data frame and returns a clean data frame. The clean data frame should have the following:

* A date column created by uniting the year, month, day and converting it to the Date class
* LATITUDE and LONGITUDE columns converted to numeric class
* In addition, write a function eq_location_clean() that cleans the LOCATION_NAME column by stripping out the country name (including the colon) and converts names to title case (as opposed to all caps). This will be needed later for annotating visualizations. This function should be applied to the raw data to produce a cleaned up version of the LOCATION_NAME column.

## Read in data

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Initial Exploratory Analysis of the Data


## eq_clean_data()


## eq_location_clean()


